---
title: "Estimativas - Frequentistas"
author: "André"
date: "12/07/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library('survival')
library('ggplot2')
source('gompertz.R')

```

## Relatório de Estimativas Frequentistas

```{r tgca}
########################## ESTIMATIVAS FREQUENTISTAS ###################

#### 1 - tgca, 2- colon, 3- melanoma, 4 - retinopathy.

### TGCA ----------
dados_tg = read.csv('dados_tg.csv', header = T)

tempos = dados_tg$tempo/365
cens = dados_tg$cens

npcure::testmz(tempos, cens)

###### Normal ----
log_veros = function(par){
  return(sum(cens*dgompertz(tempos, par[1], par[2], ln = T) +
               (1 - cens)*pgompertz(tempos, par[1], par[2], ln = T, lower.tail = F)))
}

par_init = c(0.05, 4)

optim_usual = optim(par_init, log_veros, 
                     control = list(fnscale = -1, maxit = 500),
                     method="L-BFGS-B", lower = c(0.0000001, 0.0000001), upper = c(Inf, Inf), hessian = T)

#optim_usual$hessian
optim_usual$par + qnorm(0.975) * (.hess_to_cov(-optim_usual$hessian) |> diag() |> sqrt())
optim_usual$par - qnorm(0.975) * (.hess_to_cov(-optim_usual$hessian) |> diag() |> sqrt())

###### Com Mistura ----
log_veros_mix = function(par){
  return(sum(cens*log(1-par[3]) + cens*dgompertz(tempos, par[1], par[2], ln = T) + 
    (1- cens)*log(par[3]  + (1-par[3])*(1 - pgompertz(tempos, a = par[1], b = par[2])))))
}

par_init = c(0.1, 4, 0.5)

optim_mix = optim(par_init, log_veros_mix, 
                     control = list(fnscale = -1, maxit = 500),
                     method="L-BFGS-B", lower = c(0.0000001, 0.0000001, 0.0000001), 
                  upper = c(Inf, Inf, 1), hessian = T)

optim_mix

optim_mix$par + qnorm(0.975) * (.hess_to_cov(-optim_mix$hessian) |> diag() |> sqrt())
optim_mix$par - qnorm(0.975) * (.hess_to_cov(-optim_mix$hessian) |> diag() |> sqrt())

###### Defeituoso ----
log_veros_def = function(par){
  return(sum(cens*flexsurv::dgompertz(tempos, par[1], par[2], log = T) +
           (1 - cens)*flexsurv::pgompertz(tempos, par[1], par[2], log = T, lower.tail = F)))
}

par_init = c(-0.05, 1)

optim_def = optim(par_init, log_veros_def, 
                     control = list(fnscale = -1, maxit = 500),
                     method="L-BFGS-B", lower = c(-Inf, 0.0001), upper = c(Inf, Inf),
                  hessian = T)

optim_def

optim_def$par + qnorm(0.975) * (.hess_to_cov(-optim_def$hessian) |> diag() |> sqrt())
optim_def$par - qnorm(0.975) * (.hess_to_cov(-optim_def$hessian) |> diag() |> sqrt())

####Df estimativas
estimativas = data.frame(a = c(optim_usual$par[1], optim_mix$par[1], optim_def$par[1]),
                         b = c(optim_usual$par[2], optim_mix$par[2], optim_def$par[2]),
                         p = c('-', optim_mix$par[3], '-'),
                         l = c(optim_usual$value, optim_mix$value, optim_def$value))
                           

xtable::xtable(estimativas, align = 'ccccc', digits = 4)

data(cancer, package="survival")

############# Gráficos e Figuras -----


#AIC;
4 + -2*optim_usual$value
4 + -2*optim_def$value
6 + -2*optim_mix$value


#Figuras

x = dados_tg$tempo/365

kaplan_meier_s = survfit(Surv(tempo/365, cens) ~ 1, data = dados_tg)

dados_km = data.frame(kaplan_meier_s$time, kaplan_meier_s$surv, kaplan_meier_s$n.event)
colnames(dados_km) = c('Tempo', 'Sobrevivência', 'Evento')


ggplot() + 
  geom_line(aes(x = Tempo, y = Sobrevivência, colour = "a", linetype = "a",
                ), data = dados_km, size = 1) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  labs(x = 'Tempo') +
  theme_minimal() +
  geom_line( 
    mapping=aes(x=x, y = flexsurv::pgompertz(x, optim_def$par[1], optim_def$par[2], lower.tail = F),
                colour = "c", linetype = "c"),
    size = 1) +
  geom_line( 
    mapping=aes(x=x, y = pgompertz(x, optim_usual$par[1], optim_usual$par[2], lower.tail = F),
                colour = "b", linetype = "b"),
    size = 1) +
  geom_line( 
    mapping=aes(x=x, y = optim_mix$par[3] + (1 - optim_mix$par[3])*pgompertz(x, optim_mix$par[1], 
                                                      optim_mix$par[2], lower.tail = F),
                colour = "d", linetype = "d"),
    size = 1) +
  ylim(0,1) +
  theme(legend.position = 'bottom', legend.text = element_text(size=12), legend.key.width= unit(1.5, 'cm'),         legend.key.height = unit(0.5, 'cm')) + 
  scale_color_manual(name = "",
                     values = c(
                       "royalblue",
                       "springgreen3",
                       'orange',
                       "brown2"),
                     labels = c("Kaplan-Meier","Usual", 
                                "Defeituoso",
                                "Com Mistura")) +
  scale_linetype_manual(name = "", values=c("solid", "twodash", 
                                            "dotted", "dashed"),
                        labels = c("Kaplan-Meier", 
                                   "Usual",
                                   "Defeituoso", 
                                   "Com Mistura"))


ggsave(filename = 'figuras/tgca_freq.pdf', units = 'in', width = 7, height = 5)
```

### Colon ----------

```{r colon}
data(cancer, package="survival")

tempos = colon$time/365
cens = colon$status

###### Normal ----
log_veros = function(par){
  return(sum(cens*dgompertz(tempos, par[1], par[2], ln = T) +
               (1 - cens)*pgompertz(tempos, par[1], par[2], ln = T, lower.tail = F)))
}

par_init = c(1000, 10000)

optim_usual = optim(par_init, log_veros, 
                    control = list(fnscale = -1, maxit = 500),
                    method="L-BFGS-B", lower = c(0.0000001, 0.0000001), upper = c(Inf, Inf),
                    hessian = T)

optim_usual

optim_usual$par + qnorm(0.975) * (.hess_to_cov(-optim_usual$hessian) |> diag() |> sqrt())
optim_usual$par - qnorm(0.975) * (.hess_to_cov(-optim_usual$hessian) |> diag() |> sqrt())

###### Com Mistura ----
log_veros_mix = function(par){
  return(sum(cens*log(1-par[3]) + cens*dgompertz(tempos, par[1], par[2], ln = T) + 
               (1- cens)*log(par[3]  + (1-par[3])*(1 - pgompertz(tempos, a = par[1], b = par[2])))))
}

par_init = c(3, 10, 0.2)

optim_mix = optim(par_init, log_veros_mix, 
                  control = list(fnscale = -1, maxit = 500),
                  method="L-BFGS-B", lower = c(0.0000001, 0.0000001, 0.0000001), upper = c(Inf, Inf, 1), hessian = T)

optim_mix

optim_mix$par + qnorm(0.975) * (.hess_to_cov(-optim_mix$hessian) |> diag() |> sqrt())
optim_mix$par - qnorm(0.975) * (.hess_to_cov(-optim_mix$hessian) |> diag() |> sqrt())

###### Defeituoso ----
log_veros_def = function(par){
  return(sum(cens*flexsurv::dgompertz(tempos, par[1], par[2], log = T) +
               (1 - cens)*flexsurv::pgompertz(tempos, par[1], par[2], log = T, lower.tail = F)))
}

par_init = c(-0.05, 1)

optim_def = optim(par_init, log_veros_def, 
                  control = list(fnscale = -1, maxit = 500),
                  method="L-BFGS-B", lower = c(-Inf, 0.0001), upper = c(Inf, Inf), hessian = T)

optim_def

optim_def$par + qnorm(0.975) * (.hess_to_cov(-optim_def$hessian) |> diag() |> sqrt())
optim_def$par - qnorm(0.975) * (.hess_to_cov(-optim_def$hessian) |> diag() |> sqrt())

############# Gráficos e Figuras -----


#AIC;
print(c(4 + -2*optim_usual$value,
4 + -2*optim_def$value,
6 + -2*optim_mix$value), digits = 12)


#Figuras

x = tempos

kaplan_meier_s = survfit(Surv(tempos, cens) ~ 1)

dados_km = data.frame(kaplan_meier_s$time, kaplan_meier_s$surv, kaplan_meier_s$n.event)
colnames(dados_km) = c('Tempo', 'Sobrevivência', 'Evento')


ggplot() + 
  geom_line(aes(x = Tempo, y = Sobrevivência, colour = "a", linetype = "a"), data = dados_km, size = 1) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  labs(x = 'Tempo') +
  theme_minimal() +
  geom_line( 
    mapping=aes(x=x, y = flexsurv::pgompertz(x, optim_def$par[1], optim_def$par[2], lower.tail = F),
                colour = "c", linetype = "c"),
    size = 1) +
  geom_line( 
    mapping=aes(x=x, y = pgompertz(x, optim_usual$par[1], optim_usual$par[2], lower.tail = F),
                colour = "b", linetype = "b"),
    size = 1) +
  geom_line( 
    mapping=aes(x=x, y = optim_mix$par[3] + (1 - optim_mix$par[3])*pgompertz(x, optim_mix$par[1], 
                                                                             optim_mix$par[2], lower.tail = F),
                colour = "d", linetype = "d"),
    size = 1) +
  ylim(0,1) +
  theme(legend.position = 'bottom', legend.text = element_text(size=12), legend.key.width= unit(1.5, 'cm'),         legend.key.height = unit(0.5, 'cm')) +
  scale_color_manual(name = "",
                     values = c(
                       "royalblue",
                       "springgreen3",
                       'orange',
                       "brown2"),
                     labels = c("Kaplan-Meier","Usual", 
                                "Defeituoso",
                                "Com Mistura")) +
  scale_linetype_manual(name = "", values=c("solid", "twodash", 
                                            "dotted", "dashed"),
                        labels = c("Kaplan-Meier", 
                                   "Usual",
                                   "Defeituoso", 
                                   "Com Mistura"))

ggsave(filename = 'figuras/colon_freq.pdf', units = 'in', width = 7, height = 5)

estimativas = data.frame(a = c(optim_usual$par[1], optim_mix$par[1], optim_def$par[1]),
                         b = c(optim_usual$par[2], optim_mix$par[2], optim_def$par[2]),
                         p = c('-', optim_mix$par[3], '-'),
                         l = c(optim_usual$value, optim_mix$value, optim_def$value))


xtable::xtable(estimativas, align = 'ccccc', digits = 4)
```

### Melanoma -------
```{r melanoma}
melanoma = read.table("melanoma.txt", header = T)

e1690 = melanoma[melanoma$STUDY == '1690' & melanoma$BRESLOW != '.',]

tempos = e1690$SURVTIME
cens = ifelse(e1690$SURVCENS == 2, 1, 0)

###### Normal ----
log_veros = function(par){
  return(sum(cens*dgompertz(tempos, par[1], par[2], ln = T) +
               (1 - cens)*pgompertz(tempos, par[1], par[2], ln = T, lower.tail = F)))
}

par_init = c(100, 1000)

optim_usual = optim(par_init, log_veros, 
                    control = list(fnscale = -1, maxit = 500),
                    method="L-BFGS-B", lower = c(0.0000001, 0.0000001), upper = c(Inf, Inf), hessian = T)

optim_usual

optim_usual$par + qnorm(0.975) * (.hess_to_cov(-optim_usual$hessian) |> diag() |> sqrt())
optim_usual$par - qnorm(0.975) * (.hess_to_cov(-optim_usual$hessian) |> diag() |> sqrt())


###### Com Mistura ----
log_veros_mix = function(par){
  return(sum(cens*log(1-par[3]) + cens*dgompertz(tempos, par[1], par[2], ln = T) + 
               (1- cens)*log(par[3]  + (1-par[3])*(1 - pgompertz(tempos, a = par[1], b = par[2])))))
}

par_init = c(0.1, 4, 0.5)

optim_mix = optim(par_init, log_veros_mix, 
                  control = list(fnscale = -1, maxit = 500),
                  method="L-BFGS-B", lower = c(0.0000001, 0.0000001, 0.0000001), upper = c(Inf, Inf, 1), hessian = T)

optim_mix
optim_mix$par + qnorm(0.975) * (.hess_to_cov(-optim_mix$hessian) |> diag() |> sqrt())
optim_mix$par - qnorm(0.975) * (.hess_to_cov(-optim_mix$hessian) |> diag() |> sqrt())

###### Defeituoso ----
log_veros_def = function(par){
  return(sum(cens*flexsurv::dgompertz(tempos, par[1], par[2], log = T) +
               (1 - cens)*flexsurv::pgompertz(tempos, par[1], par[2], log = T, lower.tail = F)))
}

par_init = c(-0.05, 1)

optim_def = optim(par_init, log_veros_def, 
                  control = list(fnscale = -1, maxit = 500),
                  method="L-BFGS-B", lower = c(-Inf, 0.0001), upper = c(Inf, Inf))

optim_def

############# Gráficos e Figuras -----


#AIC;
4 + -2*optim_usual$value
4 + -2*optim_def$value
6 + -2*optim_mix$value


#Figuras

x = tempos

kaplan_meier_s = survfit(Surv(tempos, cens) ~ 1)

dados_km = data.frame(kaplan_meier_s$time, kaplan_meier_s$surv, kaplan_meier_s$n.event)
colnames(dados_km) = c('Tempo', 'Sobrevivência', 'Evento')

ggplot() + 
  geom_line(aes(x = Tempo, y = Sobrevivência, colour = "a", linetype = "a"), data = dados_km, size = 1) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  labs(x = 'Tempo') +
  theme_minimal() +
  geom_line( 
    mapping=aes(x=x, y = flexsurv::pgompertz(x, optim_def$par[1], optim_def$par[2], lower.tail = F),
                colour = "c", linetype = "c"),
    size = 1) +
  geom_line( 
    mapping=aes(x=x, y = pgompertz(x, optim_usual$par[1], optim_usual$par[2], lower.tail = F),
                colour = "b", linetype = "b"),
    size = 1) +
  geom_line( 
    mapping=aes(x=x, y = optim_mix$par[3] + (1 - optim_mix$par[3])*pgompertz(x, optim_mix$par[1], 
                                                                             optim_mix$par[2], lower.tail = F),
                colour = "d", linetype = "d"),
    size = 1) +
  ylim(0,1) +
  theme(legend.position = 'bottom', legend.text = element_text(size=12), legend.key.width= unit(1.5, 'cm'),         legend.key.height = unit(0.5, 'cm')) +
  scale_color_manual(name = "",
                     values = c(
                       "royalblue",
                       "springgreen3",
                       'orange',
                       "brown2"),
                     labels = c("Kaplan-Meier","Usual", 
                                "Defeituoso",
                                "Com Mistura")) +
  scale_linetype_manual(name = "", values=c("solid", "twodash", 
                                            "dotted", "dashed"),
                        labels = c("Kaplan-Meier", 
                                   "Usual",
                                   "Defeituoso", 
                                   "Com Mistura"))

ggsave(filename = 'figuras/melanoma_freq.pdf', units = 'in', width = 7, height = 5)

estimativas = data.frame(a = c(optim_usual$par[1], optim_mix$par[1], optim_def$par[1]),
                         b = c(optim_usual$par[2], optim_mix$par[2], optim_def$par[2]),
                         p = c('-', optim_mix$par[3], '-'),
                         l = c(optim_usual$value, optim_mix$value, optim_def$value))


xtable::xtable(estimativas, align = 'ccccc', digits = 4)
```

### Diabetic -------

tempos = diabetic$time/12
cens = diabetic$status

npcure::testmz(tempos, cens)
     
###### Normal ----
log_veros = function(par){
  return(sum(cens*dgompertz(tempos, par[1], par[2], ln = T) +
               (1 - cens)*pgompertz(tempos, par[1], par[2], ln = T, lower.tail = F)))
}

par_init = c(1000, 10000)

optim_usual = optim(par_init, log_veros, 
                    control = list(fnscale = -1, maxit = 500),
                    method="L-BFGS-B", lower = c(0.0000001, 0.0000001), upper = c(Inf, Inf))

optim_usual

###### Com Mistura ----
log_veros_mix = function(par){
  return(sum(cens*log(1-par[3]) + cens*dgompertz(tempos, par[1], par[2], ln = T) + 
               (1- cens)*log(par[3]  + (1-par[3])*(1 - pgompertz(tempos, a = par[1], b = par[2])))))
}

par_init = c(10, 100, 0.5)

optim_mix = optim(par_init, log_veros_mix, 
                  control = list(fnscale = -1, maxit = 500),
                  method="L-BFGS-B", lower = c(0.0000001, 0.0000001, 0.0000001), upper = c(Inf, Inf, 1))

optim_mix

###### Defeituoso ----
log_veros_def = function(par){
  return(sum(cens*flexsurv::dgompertz(tempos, par[1], par[2], log = T) +
               (1 - cens)*flexsurv::pgompertz(tempos, par[1], par[2], log = T, lower.tail = F)))
}

par_init = c(-0.05, 1)

optim_def = optim(par_init, log_veros_def, 
                  control = list(fnscale = -1, maxit = 500),
                  method="L-BFGS-B", lower = c(-Inf, 0.0001), upper = c(Inf, Inf))

optim_def

#veros

############# Gráficos e Figuras -----


#AIC;
4 + -2*optim_usual$value
4 + -2*optim_def$value
6 + -2*optim_mix$value


#Figuras

x = tempos

kaplan_meier_s = survfit(Surv(tempos, cens) ~ 1)

dados_km = data.frame(kaplan_meier_s$time, kaplan_meier_s$surv, kaplan_meier_s$n.event)
colnames(dados_km) = c('Tempo', 'Sobrevivência', 'Evento')


ggplot() + 
  geom_line(aes(x = Tempo, y = Sobrevivência, colour = "a", linetype = "a"), data = dados_km, size = 1) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  labs(x = 'Tempo') +
  theme_minimal() +
  geom_line( 
    mapping=aes(x=x, y = flexsurv::pgompertz(x, optim_def$par[1], optim_def$par[2], lower.tail = F),
                colour = "c", linetype = "c"),
    size = 1) +
  geom_line( 
    mapping=aes(x=x, y = pgompertz(x, optim_usual$par[1], optim_usual$par[2], lower.tail = F),
                colour = "b", linetype = "b"),
    size = 1) +
  geom_line( 
    mapping=aes(x=x, y = optim_mix$par[3] + (1 - optim_mix$par[3])*pgompertz(x, optim_mix$par[1], 
                                                                             optim_mix$par[2], lower.tail = F),
                colour = "d", linetype = "d"),
    size = 1) +
  ylim(0,1) +
  theme(legend.position = 'bottom', legend.text = element_text(size=12), legend.key.width= unit(1.5, 'cm'),         legend.key.height = unit(0.5, 'cm')) +
  scale_color_manual(name = "",
                     values = c(
                       "royalblue",
                       "springgreen3",
                       'orange',
                       "brown2"),
                     labels = c("Kaplan-Meier","Usual", 
                                "Defeituoso",
                                "Com Mistura")) +
  scale_linetype_manual(name = "", values=c("solid", "twodash", 
                                            "dotted", "dashed"),
                        labels = c("Kaplan-Meier", 
                                   "Usual",
                                   "Defeituoso", 
                                   "Com Mistura"))

ggsave(filename = 'figuras/diabetic_freq.pdf', units = 'in', width = 7, height = 5)

estimativas = data.frame(a = c(optim_usual$par[1], optim_mix$par[1], optim_def$par[1]),
                         b = c(optim_usual$par[2], optim_mix$par[2], optim_def$par[2]),
                         p = c('-', optim_mix$par[3], '-'),
                         l = c(optim_usual$value, optim_mix$value, optim_def$value))


xtable::xtable(estimativas, align = 'ccccc', digits = 4)

### Ovarian -------

bc = flexsurv::bc
# tempos = bc$rectime/365
# cens = bc$censrec

# tempos = stanford2$time/365
# cens = stanford2$status

tempos = ovarian$futim/265
cens = ovarian$fustat

###### Normal ----
log_veros = function(par){
  return(sum(cens*dgompertz(tempos, par[1], par[2], ln = T) +
               (1 - cens)*pgompertz(tempos, par[1], par[2], ln = T, lower.tail = F)))
}

par_init = c(100, 1000)

optim_usual = optim(par_init, log_veros, 
                    control = list(fnscale = -1, maxit = 500),
                    method="L-BFGS-B", lower = c(0.0000001, 0.0000001), upper = c(Inf, Inf))

optim_usual

###### Com Mistura ----
log_veros_mix = function(par){
  return(sum(cens*log(1-par[3]) + cens*dgompertz(tempos, par[1], par[2], ln = T) + 
               (1- cens)*log(par[3]  + (1-par[3])*(1 - pgompertz(tempos, a = par[1], b = par[2])))))
}

par_init = c(0.05, 2, 0.5)

optim_mix = optim(par_init, log_veros_mix, 
                  control = list(fnscale = -1, maxit = 500),
                  method="L-BFGS-B", lower = c(0.0000001, 0.0000001, 0.0000001), upper = c(Inf, Inf, 1))

optim_mix

###### Defeituoso ----
log_veros_def = function(par){
  return(sum(cens*flexsurv::dgompertz(tempos, par[1], par[2], log = T) +
               (1 - cens)*flexsurv::pgompertz(tempos, par[1], par[2], log = T, lower.tail = F)))
}

par_init = c(-0.05, 1)

optim_def = optim(par_init, log_veros_def, 
                  control = list(fnscale = -1, maxit = 500),
                  method="L-BFGS-B", lower = c(-Inf, 0.0001), upper = c(Inf, Inf))

optim_def

#veros

############# Gráficos e Figuras -----


#AIC;
4 + -2*optim_usual$value
4 + -2*optim_def$value
6 + -2*optim_mix$value


#Figuras

x = tempos

kaplan_meier_s = survfit(Surv(tempos, cens) ~ 1)

dados_km = data.frame(kaplan_meier_s$time, kaplan_meier_s$surv, kaplan_meier_s$n.event)
colnames(dados_km) = c('Tempo', 'Sobrevivência', 'Evento')


ggplot() + 
  geom_line(aes(x = Tempo, y = Sobrevivência, colour = "a", linetype = "a"), data = dados_km, size = 1) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  labs(x = 'Tempo') +
  theme_minimal() +
  geom_line( 
    mapping=aes(x=x, y = flexsurv::pgompertz(x, optim_def$par[1], optim_def$par[2], lower.tail = F),
                colour = "c", linetype = "c"),
    size = 1) +
  geom_line( 
    mapping=aes(x=x, y = pgompertz(x, optim_usual$par[1], optim_usual$par[2], lower.tail = F),
                colour = "b", linetype = "b"),
    size = 1) +
  geom_line( 
    mapping=aes(x=x, y = optim_mix$par[3] + (1 - optim_mix$par[3])*pgompertz(x, optim_mix$par[1], 
                                                                             optim_mix$par[2], lower.tail = F),
                colour = "d", linetype = "d"),
    size = 1) +
  ylim(0,1) +
  theme(legend.position = 'bottom', legend.text = element_text(size=12), legend.key.width= unit(1.5, 'cm'),         legend.key.height = unit(0.5, 'cm')) +
  scale_color_manual(name = "",
                     values = c(
                       "royalblue",
                       "springgreen3",
                       'orange',
                       "brown2"),
                     labels = c("Kaplan-Meier","Usual", 
                                "Defeituoso",
                                "Com Mistura")) +
  scale_linetype_manual(name = "", values=c("solid", "twodash", 
                                            "dotted", "dashed"),
                        labels = c("Kaplan-Meier", 
                                   "Usual",
                                   "Defeituoso", 
                                   "Com Mistura"))

ggsave(filename = 'figuras/ovarian_freq.pdf', units = 'in', width = 7, height = 5)

estimativas = data.frame(a = c(optim_usual$par[1], optim_mix$par[1], optim_def$par[1]),
                         b = c(optim_usual$par[2], optim_mix$par[2], optim_def$par[2]),
                         p = c('-', optim_mix$par[3], '-'),
                         l = c(optim_usual$value, optim_mix$value, optim_def$value))


xtable::xtable(estimativas, align = 'ccccc', digits = 4)
